Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
trying data subsets

lances_M %>%
  dplyr::group_by(site) %>%
  dplyr::summarise(mean=mean(sock_bdiam, na.rm = TRUE), n = sum(!is.na(sock_bdiam)))
```

@@

cor(lances_M$sock_sdiam,lances_M$width, use= "pairwise.complete.obs", method = "pearson")
cor(lances_M$sock_sdiam,lances_M$width, use= "pairwise.complete.obs", method = "spearman")
```
```{r replication corr test, include=TRUE, echo=FALSE}
ggpairs(lances_M[complete.cases(lances_M),], columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8v2.png"))

>>>>

lances_M %>%
  dplyr::group_by(site) %>%
  dplyr::summarise(mean=mean(sock_bdiam, na.rm = TRUE), n = sum(!is.na(sock_bdiam)))

blade %>%
  dplyr::group_by(site) %>%
  dplyr::summarise(mean=mean(blade_length, na.rm = TRUE), n = sum(!is.na(blade_length)))
```

@@

cor(lances_M$sock_sdiam,lances_M$width, use= "pairwise.complete.obs", method = "pearson")
cor(lances_M$sock_sdiam,lances_M$width, use= "pairwise.complete.obs", method = "spearman")
```
Try recreating figure on different data subsets:

```{r replication corr test, include=TRUE, echo=FALSE}
ggpairs(lances_M[complete.cases(lances_M),], columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_complete_cases_manual.png"))

ggpairs(blade, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blade.png"))

ggpairs(socket, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_socket.png"))

ggpairs(total, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blades_and_sockets.png"))
